GEE models

### 2017-10-15 doc/esm.Rmd
described DAG colors

sfig_consort <- sfig('consort', 'CONSORT diagram of sample size at each examination visit for the main PROMISE cohort in addition of the sample size determination for the present analysis.')
sfig_dag_isi <- sfig("dag_isi", "Directed acyclic graph taken from DAGitty (DAGitty.net) for the potential causal pathway between NEFA and ISI. DAGitty recommended a minimal adjustment of waist, sex, and MET (physical activity).")
sfig_dag_issi2 <- sfig("dag_issi2", "Directed acyclic graph taken from DAGitty (DAGitty.net) for the potential causal pathway between NEFA and ISSI-2. DAGitty recommended a minimal adjustment of waist, ethnicity, and MET (physical activity).")
sfig_corr_conc <- sfig('corr_conc', 'Pearson correlation heatmap of non-esterified fatty acids (*nmol/mL*) and basic PROMISE participant characteristics for the baseline visit (2004-2006). Darkness of the colour indicates the magnitude of the correlation, with orange indicating positive and blue indicating negative correlations.')
sfig_corr_pct <- sfig('corr_pct', 'Pearson correlation heatmap of non-esterified fatty acids (*mol%*) and basic PROMISE participant characteristics for the baseline visit (2004-2006). Darkness of the colour indicates the magnitude of the correlation, with orange indicating positive and blue indicating negative correlations.')
sfig_gee_adj_nowaist <- sfig('gee_adj_nowaist', 'Longitudinal associations of individual non-esterified fatty acids (mol% and nmol/mL) with insulin sensitivity and beta-cell function over the 6 years in the PROMISE cohort. Generalized estimating equation models were fully adjusted, *excluding waist circumference*. X-axis values represent a percent difference in the outcome per SD increase in the fatty acid. P-values were adjusted for the BH false discovery rate, with each increase in dot size and blackness representing a p-value significance of p>0.05, p<0.05, and p<0.01.')
```

>>>>

sfig_consort <- sfig('consort', 'CONSORT diagram of sample size at each examination visit for the main PROMISE cohort in addition of the sample size determination for the present analysis.')
sfig_dag_isi <- sfig("dag_isi", "Directed acyclic graph taken from DAGitty (DAGitty.net) for the potential causal pathway between NEFA and ISI. Node and arrow description: Green with a triangle is the exposure; blue with a line/I is the outcome; empty blue is an ancestor of the outcome; empty green is an ancestor of the exposure; and empty red is an ancestor of both the outcome and the exposure; green arrow is on causal pathway; red arrow is a biasing pathway; black arrow is not along the pathway from the exposure to the outcome. DAGitty recommended a minimal adjustment of waist, sex, and MET (physical activity).")
sfig_dag_issi2 <- sfig("dag_issi2", "Directed acyclic graph taken from DAGitty (DAGitty.net) for the potential causal pathway between NEFA and ISSI-2. Node and arrow description: Green with a triangle is the exposure; blue with a line/I is the outcome; empty blue is an ancestor of the outcome; empty green is an ancestor of the exposure; and empty red is an ancestor of both the outcome and the exposure; green arrow is on causal pathway; red arrow is a biasing pathway; black arrow is not along the pathway from the exposure to the outcome. DAGitty recommended a minimal adjustment of waist, ethnicity, and MET (physical activity).")
sfig_corr_conc <- sfig('corr_conc', 'Pearson correlation heatmap of non-esterified fatty acids (*nmol/mL*) and basic PROMISE participant characteristics for the baseline visit (2004-2006). Darkness of the colour indicates the magnitude of the correlation, with orange indicating positive and blue indicating negative correlations.')
sfig_corr_pct <- sfig('corr_pct', 'Pearson correlation heatmap of non-esterified fatty acids (*mol%*) and basic PROMISE participant characteristics for the baseline visit (2004-2006). Darkness of the colour indicates the magnitude of the correlation, with orange indicating positive and blue indicating negative correlations.')
sfig_gee_adj_nowaist <- sfig('gee_adj_nowaist', 'Longitudinal associations of individual non-esterified fatty acids (mol% and nmol/mL) with insulin sensitivity and beta-cell function over the 6 years in the PROMISE cohort. Generalized estimating equation models were fully adjusted, *excluding waist circumference*. X-axis values represent a percent difference in the outcome per SD increase in the fatty acid. P-values were adjusted for the BH false discovery rate, with each increase in dot size and blackness representing a p-value significance of p>0.05, p<0.05, and p<0.01.')
```
